### 2018-09-11 Paper/Paper.tex
Added bib file

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
\usepackage[subfolder,cleanup]{gnuplottex}
\usepackage{tikz}
\usepackage{pgfplots}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
%\usepackage{hyperref}

@@

@@

\begin{figure}[htbp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
f(x) = m * x + c
fit [0.03:0.6] f(x) '../sdata.dat' u 1:(log($2)) via m, c
set grid
set ytics 0.1
set xl '$s$'
set yl 'Spread'
plot '../sdata.dat' u 1:2 w p pt 7 ps 0.4 t 'Data', \
exp(f(x)) t '$\exp(-0.513865s + 0.00203874)$'
\end{gnuplot}
\caption{}
\label{fig:}
\end{figure}

@@

\newpage
\begin{thebibliography}{99}
\bibitem{silfvast}
Laser Fundamentals

\bibitem{ferreira}
Nonlinear Effects in Optical Fibers

\end{thebibliography}
\end{document}

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
\usepackage[subfolder,cleanup]{gnuplottex}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
%\usepackage{hyperref}
\usepackage{biblatex}

\bibliography{Ref.bib}

@@

\begin{align*}
G(A) &= \left( \frac{W_0 \left( a E e^{E}\right)}{E} \right)^{1/2} A.
\end{align*}

\begin{align*}
D(A) &= \FTi{e^{i s^2 \omega^2} \FT{A}}
\end{align*}

\begin{align*}
F(A) &= A e^{i b |A|^2},
\end{align*}

\begin{align*}
L(A) &= h A,
\end{align*}

\begin{align*}
M(A) &= e^{-T^2 / 2} A
\end{align*}

\begin{align*}
a = e^{g_0 L_g} \quad s^2 = \frac{\beta_2 L_D}{2 T_M^2}, \quad b = \gamma L_F \frac{\Es}{T_M}, \quad h = C e^{-\alpha L}
\end{align*}

@@

\begin{figure}[htbp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
f(x) = m * x + c
fit f(x) '../sdata.dat' u 1:(log($2)) via m, c
set grid
set ytics 0.1
set xl '$s$'
set yl 'Spread'
plot '../sdata.dat' u 1:2 w p pt 7 ps 0.4 t 'Data', \
exp(f(x)) t '$\exp(-0.521294s + 0.00365752)$'
\end{gnuplot}
\caption{}
\label{fig:}
\end{figure}

@@

\newpage
\appendix
\section{Numbers}

\begin{table}
\begin{tabular}{|l|l|}
\hline
Parameter & Value \\
\hline
$\beta_2^g L_D$ & $10$--$2000 \text{ps}^2$ \\
$g_0$ & $1$--$10 \text{m}^{-1}$ \\
$\beta_2^f$ & $20$--$50 \text{ps}^2/ \text{km}$ \\
$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \\
$\Es$ & $10^4 \text{pJ}$ \\
$L_g$ & $3 \text{m}$ \\
\hline
\end{tabular}
\end{table}

\newpage
\printbibliography
\end{document}
